Adaptive Scheduling of Scientific Workflows\\ \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-05-02 main.tex
various changes in first sections

@@

@@

    \section{Related work}

@@

    \subsection{Model}

>>>>

    Only mapping tasks to processors is not enough.
    Reusing processors is important to achieve good makespans.

    HEFT is one of the most popular heuristics (cite a review).
    However, existing HEFT variations do not take memory sizes into consideration (\skug{check in related work if true!}).

    In this paper, we formulate the problem that takes memories into consideration.
    We propose three HEFT-based heuristics that take memory size into account: \heftbl, \heftblc, and \heftmm.
    The difference is the way they order tasks for scheduling.
    We compare our heuristics to a baseline HEFT variant that does not take memory sizes into account.

    We find that our heuristics are able to schedule all workflows correctly, and produce makespans similar to the baseline.

@@

    \skug{TODO:unify the notation with the table!!}

@@

    \section{Related work}
    \skug{problem: this is written for the old heuristic - parititioning-based heuristic to solvea dynamic problem! it is irrelevant to heft}

@@
